Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-08 WSSSPE1_report/WSSSPE1_summary_report.tex
Fix typo in note.
ordering authors, other misc things

\author{Bruce Berriman$^{(1)}$, Sou-Cheng T. Choi$^{(2)}$, Marcus D. Hanwell$^{(3)}$, James Hetherington$^{(4)}$, James Howison$^{(5)}$, Daniel S. Katz$^{(6)}$, Hilmar Lapp$^{(7)}$, Frank L\"{o}ffler$^{(8)}$, Ketan Maheshwari$^{(9)}$, Shel Swenson$^{(10)}$,  Andy R. Terrel$^{(11)}$, Matthew Turk$^{(12)}$,  Colin Venters$^{(13)}$, Nancy Wilkins-Diehr$^{(14)}$}
\note{Authors, please add/check middle initials and affliations.  For now, the order is alphabetical for now  because Choi does not know how to count...}

\thanks{{}$^{(1)}$ xxx}
%
\thanks{{}$^{(2)}$ NORC at the University of Chicago and the Illinois Institute of Technology, Chicago, IL, USA (\url{sctchoi@uchicago.edu}}
% 
\thanks{{}$^{(3)}$ xxx}
%
\thanks{{}$^{(4)}$ xxx}
%
\thanks{{}$^{(5)}$ xxx}
%
\thanks{{}$^{(6)}$ National Science Foundation, Arlington, VA, USA}
%
\thanks{{}$^{(7)}$ xxx}
%
\thanks{{}$^{(8)}$ xxx}
%
\thanks{{}$^{(9)}$ xxx}
%
\thanks{{}$^{(10)}$ xxx}
%
\thanks{{}$^{(11)}$ xxx}
%
\thanks{{}$^{(12)}$ xxx}
%
\thanks{{}$^{(13)}$ xxx}
%
\thanks{{}$^{(14)}$ xxx}

@@

The literature below, suggested by attendees, addresses both non-scientific
software projects, as well as scientific projects.  The selections address both
descriptive and prescriptive approaches to communities. \note{Choi: Do we need to itemize the reference numbers below? Please collapse them into a comma seperated list with a short description for all or each of the papers.
}

\begin{itemize}
\item \cite{howison_scientific_2011}
\item \cite{citeulike:11831265}
\item \cite{citeulike:7888211}
\item \cite{citeulike:478633}
\item \cite{opac-b1134063}
\item \cite{DBLP:conf/cscw/HowisonH11}
\item \cite{DBLP:conf/cscw/2011}
\item \cite{Trapani:2011}
\item \cite{Allsopp:2012}
\item \cite{1749-4699-6-1-015010}
\item \cite{Turk:2013:SCH:2484762.2484782}
\end{itemize}

@@

@@

\note{So far this reads a lot like a collection of thoughts only, without ``red line''.}
\note{Dan: assuming the previous note is from FL, what do you propose?}
The question of what was meant by ``sustainability'' in the context of software
came up in many different parts of the workshop, specifically in the first
keynote (\S\ref{sec:keynote1}), the Developing and Maintaining Software panel,
and the Policy panel.

@@

\subsection{Career Tracks for Scientific Software Developers} \label{sec:career-tracks}

@@

>>>>

\author{Daniel S. Katz$^{(1)}$, Hilmar Lapp$^{(2)}$, Ketan Maheshwari$^{(3)}$, Frank L\"{o}ffler$^{(4)}$, Matthew Turk$^{(5)}$, Marcus D. Hanwell$^{(6)}$, Nancy Wilkins-Diehr$^{(7)}$, James Hetherington$^{(9)}$, James Howison$^{(9)}$, Sou-Cheng T. Choi$^{(10)}$, Shel Swenson$^{(11)}$,  Bruce Berriman$^{(12)}$, Andy R. Terrel$^{(13)}$, Colin Venters$^{(14)}$}
\note{Authors, please add/check middle initials and affiliations.}

\thanks{{}$^{(1)}$ National Science Foundation, Arlington, VA, USA; Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; \url{d.katz@ieee.org}}
%
\thanks{{}$^{(2)}$ xxx}
%
\thanks{{}$^{(3)}$ xxx}
%
\thanks{{}$^{(4)}$ xxx}
%
\thanks{{}$^{(5)}$ xxx}
%
\thanks{{}$^{(7)}$ xxx}
%
\thanks{{}$^{(8)}$ xxx}
%
\thanks{{}$^{(9)}$ xxx}
%
\thanks{{}$^{(10)}$ NORC at the University of Chicago and the Illinois Institute of Technology, Chicago, IL, USA; (\url{sctchoi@uchicago.edu}}
% 
\thanks{{}$^{(11)}$ xxx}
%
\thanks{{}$^{(12)}$ xxx}
%
\thanks{{}$^{(13)}$ xxx}
%
\thanks{{}$^{(14)}$ xxx}

@@

The literature below, suggested by attendees, addresses both non-scientific
software projects, as well as scientific projects.  The selections address both
descriptive and prescriptive approaches to communities. 
\begin{itemize}
\item \cite{howison_scientific_2011}
\item \cite{citeulike:11831265}
\item \cite{citeulike:7888211}
\item \cite{citeulike:478633}
\item \cite{opac-b1134063}
\item \cite{DBLP:conf/cscw/HowisonH11}
\item \cite{DBLP:conf/cscw/2011}
\item \cite{Trapani:2011}
\item \cite{Allsopp:2012}
\item \cite{1749-4699-6-1-015010}
\item \cite{Turk:2013:SCH:2484762.2484782}
\end{itemize}

@@

Two issues were raised in a number of the workshops sessions, defining sustainability and career paths.  This section brings those discussions together.

@@

%\note{So far this reads a lot like a collection of thoughts only, without ``red line''.}
%\note{Dan: assuming the previous note is from FL, what do you propose?}
The question of what was meant by ``sustainability'' in the context of software
came up in many different parts of the workshop, specifically in the first
keynote (\S\ref{sec:keynote1}), the Developing and Maintaining Software panel,
and the Policy panel.

@@

\subsection{Career Tracks for Scientific Software Developers} \note{lead: Daniel S. Katz} \label{sec:defining-sustainability}\label{sec:career-tracks}

@@

\katznote{discuss sustainability survey}
